Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-08-06 article.hid2-ub-cicd.ppam24.tex
setup article.template workflow
#1

\begin{document}
\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{}
\author{Luca Berti (formerly)\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\ \and
Maryam Maslek Elayam \inst{1} \and
Philippe Pinçon \inst{1} \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\authorrunning{V. Chabannes et al.}

@@

The Ktirio Urban Building (KUB) pilot in CoE HiDALGO2 aims to leverage high-performance computing to enhance city energy simulation for better energy management and air quality assessment. Advanced simulation tools predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales. These simulations support detailed individual building-level analysis and extend to broader urban environments, influencing urban planning and policy-making.

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{images/city-grenoble-terrain.png}
}

@@

In the urban modeling process, particularly in generating building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role. CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes. This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.

@@

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the tiles used are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{images/city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

@@

\begin{figure}[htbp]
\centering
\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-whole.png}
}
\hfill
\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomB.png}
}\\
\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomA.png}
}
\hfill
\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomC.png}
}
\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
\label{fig:city-ny-largescale}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{images/solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{images/solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{images/solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{images/view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot large-scaleale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/ub-hpcops.pdf}
    \caption{Urban Building HPC Ops workflow}
    \label{fig:kub-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth}  % Adjust 'R' and width as needed
  \centering
  \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{images/kub-scalability.png}
    \label{fig:scalability}
  }\end{subfloat}
  \\
  \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{images/kub-bencharkings-execution.png}
    \label{fig:execution-breakdown}
  }\end{subfloat}
  \caption{Detailed performance metrics for scalability and execution on EuroHPC systems}
  \label{fig:combined-metrics}
\end{wrapfigure}
The pipeline's simulation part scales almost linearly, which is expected as the buildings are not coupled together in the model currently used for the simulation. On the other hand, the total execution of the pilot's pipeline does not scale; as more nodes are employed, the performance degrades.

@@

Our next steps include \textit{(i)} enabling tasks-based parallelism using the C++ framework Specx, see~\cite{cardosi_specx_2022}; \textit{(ii)} improving the modeling and simulation components, including mesh generation, handling of vegetation and urban furniture, and enabling view factors as well as providing a variety of configurable building energy models; \textit{(iii)} enhanced parallel strategies particularly in terms of partitioning and improved large scale I/O.

>>>>

\usepackage{ifthen}

\newcommand{\imagedir}{./} % default directory
% Shell command to check if a directory exists
\immediate\write18{if [ -d "./images" ]; then echo "\\\\renewcommand{\\imagedir}{./images/}"; fi > checkdir.tex}

% Input the output commands from the shell
\InputIfFileExists{checkdir.tex}{}{}

\begin{document}

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}

\authorrunning{V. Chabannes et al.}

@@

The Ktirio Urban Building (KUB) pilot in CoE HiDALGO2 aims to leverage high-performance computing to enhance city energy simulation for better energy management and air quality assessment. Advanced simulation tools predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales. These simulations support detailed individual building-level analysis and extend to broader urban environments, influencing urban planning and policy-making. KUB is part of the platform Ktirio~\cite{cemosis_ktirio_2024} which itself is based on Feel++~\cite{christophe_prudhomme_feelppfeelpp_2024}.

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{\imagedir kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{\imagedir city-grenoble-terrain.png}
}

@@

In the urban modeling process, particularly in generating building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role. CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes. This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs~\cite{loriot_polygon_2024}, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.

@@

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the tiles used are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired~\cite{loriot_polygon_2024} to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{\imagedir city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

@@

\begin{figure}[htbp]
\centering
\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-whole.png}
}
\hfill
\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomB.png}
}\\
\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomA.png}
}
\hfill
\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomC.png}
}
\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
\label{fig:city-ny-largescale}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{\imagedir view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{\imagedir ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{\imagedir ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{0.6\textwidth}  % Adjust 'R' and width as needed
  \centering
  \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{\imagedir kub-scalability.png}
    \label{fig:scalability}
  }\end{subfloat}
  \\
  \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
    \includegraphics[width=0.9\linewidth]{\imagedir kub-bencharkings-execution.png}
    \label{fig:execution-breakdown}
  }\end{subfloat}
  \caption{Detailed performance metrics for scalability and execution on EuroHPC systems}
  \label{fig:combined-metrics}
\end{wrapfigure}
The pipeline's simulation part scales almost linearly, which is expected as the buildings are not coupled together in the model currently used for the simulation. On the other hand, the total execution of the pilot's pipeline does not scale; as more nodes are employed, the performance degrades.

@@

Our next steps include \textit{(i)} enabling tasks-based parallelism using the C++ framework Specx, see~\cite{cardosi_specx_2022}; \textit{(ii)} improving the modeling and simulation components, including mesh generation, handling of vegetation and urban furniture, and enabling view factors as well as providing a variety of configurable building energy models; \textit{(iii)} enhanced parallel strategies particularly in terms of partitioning and improved large scale I/O; and of course \textit{(iv)} pursue our benchmarking activities on EuroHPC JU supercomputers.
